The {\em Diff} MILP model and PCA for \\ {\em real-time} DNN robustness certification

### 2025-12-11 CAV 2026/experiments.tex
global
update the table
TYPO

	CIFAR-C1  & Bound $\downarrow$ & ? & 27.15 & 25.94 & {\bf 24.52}& 23.29
    \\
	TO=1000s & $\%$ of gap $\downarrow$ & ? & 28 $\%$ & 24 $\%$& 
	{\bf 20} $\%$ & 15 $\%$
	\\\hline

	TO=14400s  & Bound $\downarrow$ & ? & 22.73 & {\bf 21.77} & 21.81 & 20.38
    \\
	 & $\%$ of gap $\downarrow$ & ? & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
		\\\hline \hline

     \end{tabular}
	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation, average over all bounds $\beta_{i,j}$. {\em Best} uses the best between our {\em Diff} and our {\em 2b+1} for each $i,j$. Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite.}
    \label{table.classical}
\end{table}

>>>>

	CIFAR-C1  & Bound $\downarrow$ & 36.57* & 27.15 & 25.94 & {\bf 24.52}& 23.29
    \\
	TO=1000s & $\%$ of gap $\downarrow$ & 55* $\%$ & 28 $\%$ & 24 $\%$& 
	{\bf 20} $\%$ & 15 $\%$
	\\\hline

	TO=14400s  & Bound $\downarrow$ & 31.53* & 22.73 & {\bf 21.77} & 21.81 & 20.38
    \\
	 & $\%$ of gap $\downarrow$ & 39* $\%$ & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
		\\\hline \hline

     \end{tabular}
	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation, average over all bounds $\beta_{i,j}$. {\em Best} uses the best between our {\em Diff} and our {\em 2b+1} for each $i,j$. Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite. * for CIFAR-C1, Vhagar failed to compute bounds for some of the cases. For such cases, we used numbers from ITNE instead (which is overperforming Vhagar in every test), so these numbers are optimistic evaluation for Vhagar.}
    \label{table.classical}
\end{table}
